---
title: "Data Cleaning"
author: "John Viviani"
date: "5/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(data.table)
library(car)
```


# Reading in the Data
```{r}
boston_final <- read.csv("~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/boston_final.csv")
portland_final <- read.csv("~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/portland_final.csv")
charleston_final <- read.csv("~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/charleston_final.csv")
nyc_final <- read.csv("~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/nyc_final.csv")

# Checking for missing data in this data frame
df_3 <- read.csv("~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/df_3.csv")

# This includes NYC; checking for missing data (line 142)
df_4 <- read.csv("~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/df_4.csv")
```


# Creating a complete data frame (contains menu, location, etc.)
```{r}
# Complete data frame with all relevant menu info.
complete_df <- do.call("rbind", list(boston_final, portland_final, charleston_final, nyc_final))

# Check for these strings, and attach the corresponding city name
complete_df %>%
  mutate(City = case_when(grepl(', MA', complete_df$Address) ~ 'Boston', 
                          grepl(', ME', complete_df$Address) ~ 'Portland', 
                          grepl(', SC', complete_df$Address) ~ 'Charleston',
                          grepl(', NY', complete_df$Address) ~ 'New York City')) -> complete_df

str(complete_df)

# Converting to character
complete_df$Address <- as.character(complete_df$Address)
complete_df$Restaurant <- as.character(complete_df$Restaurant)
complete_df$Food <- as.character(complete_df$Food)
complete_df$Cuisine <- as.character(complete_df$Cuisine)

# Cleaning the price column + converting to numeric
complete_df$Price <- as.numeric(gsub("[[:alpha:]|[:blank:]|,|+]", "", complete_df$Price))
```


# Checking for missing data in df_3
```{r}
cmp_df <- data.frame(unique(complete_df$Address))
df3_new <- data.frame(unique(df_3$Address))

# converting from factor to character
cmp_df$unique.complete_df.Address. <- as.character(cmp_df$unique.complete_df.Address.)

df3_new$unique.df_3.Address. <- as.character(df3_new$unique.df_3.Address.)

#rename
colnames(cmp_df) <- c("place")
colnames(df3_new) <- c("place")

# verifying structure is correct (character)
str(cmp_df)
str(df3_new)

# 7 rows of missing data
## This is because these restaurants did not have menu data available to pull
## Need to remove from data; will use complete_df (111 restaurants) going forward
missing_data <- anti_join(df3_new, cmp_df, by = "place")
missing_data
```


# Fixing an Address String and Saving the Complete Data Frame
```{r}
# Checking for a particular address string
complete_df[complete_df$Address %like% "Location",]

# Fixing the address (says "Location Varies", but still pulls correct address info. Updating address.)
complete_df <- complete_df %>% 
  mutate(., Address = recode(Address, "'Location Varies Boston, MA, 02201' = '15 Court Square, Boston, MA 02108'"))

#write.csv(complete_df, "~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/complete_df.csv")

# this will preserve the proper format for the variables
#saveRDS(complete_df, "~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/complete_df")

# This data frame has each unique restaurant address to use for mapping in the app.
complete_df_app <- data.frame(unique(complete_df[,c(2,3,6:9)]))

#write.csv(complete_df_app, "~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/complete_df_app.csv")

# this will preserve the proper format for the variables
#saveRDS(complete_df_app, "~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/complete_df_app")
```

The address pulled is labeled as "Location Varies Boston, MA, 02201"; however, the actual address being pulled is "15 Court Square, Boston, MA 02108". I updated the address in the data frame so the map in the app will display this address instead.

```{r}
n_occur <- data.frame(table(complete_df_app$Restaurant))
# finding restaurants with the same name
n_occur[n_occur$Freq > 1,]

complete_df_app2 <- complete_df_app

# appending part of address to distinguish between them
complete_df_app2[94,3] <- "Captain D's 1936"
complete_df_app2[100,3] <- "Captain D's 4008"
complete_df_app2[104,3] <- "Captain D's 5130"
complete_df_app2[106,3] <- "Captain D's 6326"
complete_df_app2[88,3] <- "Charleston Crab House 145"
complete_df_app2[101,3] <- "Charleston Crab House 41"
complete_df_app2[5,3] <- "Legal Sea Foods 100"
complete_df_app2[26,3] <- "Legal Sea Foods 255"
complete_df_app2[27,3] <- "Legal Sea Foods 26"
complete_df_app2[89,3] <- "Pearlz Oyster Bar 153"
complete_df_app2[110,3] <- "Pearlz Oyster Bar 9"
complete_df_app2[85,3] <- "The Boathouse 10"
complete_df_app2[98,3] <- "The Boathouse 38"
complete_df_app2[105,3] <- "The Boathouse 549"
complete_df_app2[93,3] <- "The Crab Shack 1901"
complete_df_app2[109,3] <- "The Crab Shack 8486"
complete_df_app2[19,3] <- "The Daily Catch 2"
complete_df_app2[37,3] <- "The Daily Catch 323"

#write.csv(complete_df_app2, "~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/complete_df_app2.csv")

# this will preserve the proper format for the variables
#saveRDS(complete_df_app2, "~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/complete_df_app2")
```


# Checking for missing data in df_4
```{r}
cmp_df <- data.frame(unique(complete_df$Address))
df4_new <- data.frame(unique(df_4$Address))

# converting from factor to character
cmp_df$unique.complete_df.Address. <- as.character(cmp_df$unique.complete_df.Address.)

df4_new$unique.df_4.Address. <- as.character(df4_new$unique.df_4.Address.)

#rename
colnames(cmp_df) <- c("place")
colnames(df4_new) <- c("place")

# verifying structure is correct (character)
str(cmp_df)
str(df4_new)

# 19 rows of missing data (12 of which are from NYC)
## This is because these restaurants did not have menu data available to pull
## Need to remove from data; will use complete_df (111 restaurants) going forward
missing_data <- anti_join(df4_new, cmp_df, by = "place")
missing_data
```


# Fixing an Address String and Saving the Complete Data Frame
```{r}
# Checking for a particular address string
complete_df[complete_df$Address %like% "Location",]

# Fixing the address (says "Location Varies", but still pulls correct address info. Updating address.)
complete_df <- complete_df %>% 
  mutate(., Address = recode(Address, "'Location Varies Boston, MA, 02201' = '15 Court Square, Boston, MA 02108'"))

# same for NYC address (Red Hook Lobster Pound)
complete_df <- complete_df %>% 
  mutate(., Address = recode(Address, "'Location Varies New York, NY, 10022' = '365 Park Ave, New York, NY 10154'"))

#write.csv(complete_df, "~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/complete_df_nyc.csv")

# this will preserve the proper format for the variables
#saveRDS(complete_df, "~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/complete_df_nyc")

# This data frame has each unique restaurant address to use for mapping in the app.
complete_df_nyc_app <- data.frame(unique(complete_df[,c(2,3,6:9)]))

# resetting the row names
row.names(complete_df_nyc_app) <- NULL

# Silver Star Restaurant is duped
complete_df_nyc_app <- complete_df_nyc_app[-131,]

#write.csv(complete_df_nyc_app, "~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/complete_df_nyc_app.csv")

# this will preserve the proper format for the variables
#saveRDS(complete_df_nyc_app, "~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/complete_df_nyc_app")
```


# Appending Parts of Address to Franchises
```{r}
n_occur <- data.frame(table(complete_df_nyc_app$Restaurant))
# finding restaurants with the same name
n_occur[n_occur$Freq > 1,]

complete_df_nyc_app2 <- complete_df_nyc_app
# resetting the row names
row.names(complete_df_nyc_app2) <- NULL

# appending part of address to distinguish between them
complete_df_nyc_app2[94,2] <- "Captain D's 1936"
complete_df_nyc_app2[100,2] <- "Captain D's 4008"
complete_df_nyc_app2[104,2] <- "Captain D's 5130"
complete_df_nyc_app2[106,2] <- "Captain D's 6326"
complete_df_nyc_app2[88,2] <- "Charleston Crab House 145"
complete_df_nyc_app2[101,2] <- "Charleston Crab House 41"
complete_df_nyc_app2[5,2] <- "Legal Sea Foods 100"
complete_df_nyc_app2[26,2] <- "Legal Sea Foods 255"
complete_df_nyc_app2[27,2] <- "Legal Sea Foods 26"
complete_df_nyc_app2[89,2] <- "Pearlz Oyster Bar 153"
complete_df_nyc_app2[110,2] <- "Pearlz Oyster Bar 9"
complete_df_nyc_app2[85,2] <- "The Boathouse 10"
complete_df_nyc_app2[98,2] <- "The Boathouse 38"
complete_df_nyc_app2[105,2] <- "The Boathouse 549"
complete_df_nyc_app2[93,2] <- "The Crab Shack 1901"
complete_df_nyc_app2[109,2] <- "The Crab Shack 8486"
complete_df_nyc_app2[19,2] <- "The Daily Catch 2"
complete_df_nyc_app2[37,2] <- "The Daily Catch 323"
complete_df_nyc_app2[184,2] <- "Ben & Jack's Steakhouse 219"
complete_df_nyc_app2[207,2] <- "Ben & Jack's Steakhouse 255"
complete_df_nyc_app2[111,2] <- "Bubba Gump Shrimp Co. 99"
complete_df_nyc_app2[148,2] <- "Bubba Gump Shrimp Co. 1501"
complete_df_nyc_app2[161,2] <- "Cafe Espanol 172"
complete_df_nyc_app2[284,2] <- "Cafe Espanol 78"
complete_df_nyc_app2[150,2] <- "Flex Mussels 154"
complete_df_nyc_app2[163,2] <- "Flex Mussels 174"
complete_df_nyc_app2[197,2] <- "Joe's Crab Shack 2349"
complete_df_nyc_app2[218,2] <- "Joe's Crab Shack 301"
complete_df_nyc_app2[63,2] <- "Luke's Lobster 75"
complete_df_nyc_app2[113,2] <- "Luke's Lobster 1"
complete_df_nyc_app2[176,2] <- "Luke's Lobster 207"
complete_df_nyc_app2[201,2] <- "Luke's Lobster 242"
complete_df_nyc_app2[209,2] <- "Luke's Lobster 26"
complete_df_nyc_app2[243,2] <- "Luke's Lobster 426"
complete_df_nyc_app2[272,2] <- "Luke's Lobster 685"
complete_df_nyc_app2[301,2] <- "Luke's Lobster 93"
complete_df_nyc_app2[155,2] <- "Red Hook Lobster Pound 16"
complete_df_nyc_app2[313,2] <- "Red Hook Lobster Pound 365"
complete_df_nyc_app2[260,2] <- "The Mermaid Inn 568"
complete_df_nyc_app2[307,2] <- "The Mermaid Inn 96"

#write.csv(complete_df_nyc_app2, "~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/complete_df_nyc_app2.csv")

# this will preserve the proper format for the variables
#saveRDS(complete_df_nyc_app2, "~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/complete_df_nyc_app2")
```