---
title: "Data Cleaning"
author: "John Viviani"
date: "5/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(data.table)
library(car)
```


# Reading in the Data
```{r}
boston_final <- read.csv("~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/boston_final.csv")
portland_final <- read.csv("~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/portland_final.csv")
charleston_final <- read.csv("~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/charleston_final.csv")

# Checking for missing data in this data frame
df_3 <- read.csv("~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/df_3.csv")
```


# Creating a complete data frame (contains menu, location, etc.)
```{r}
# Complete data frame with all relevant menu info.
complete_df <- do.call("rbind", list(boston_final, portland_final, charleston_final))

# Check for these strings, and attach the corresponding city name
complete_df %>%
  mutate(City = case_when(grepl(', MA', complete_df$Address) ~ 'Boston', 
                          grepl(', ME', complete_df$Address) ~ 'Portland', 
                          grepl(', SC', complete_df$Address) ~ 'Charleston')) -> complete_df

str(complete_df)

# Converting to character
complete_df$Address <- as.character(complete_df$Address)
complete_df$Restaurant <- as.character(complete_df$Restaurant)
complete_df$Food <- as.character(complete_df$Food)
complete_df$Cuisine <- as.character(complete_df$Cuisine)

# Cleaning the price column + converting to numeric
complete_df$Price <- as.numeric(gsub("[[:alpha:]|[:blank:]|,|+]", "", complete_df$Price))
```


# Checking for missing data
```{r}
cmp_df <- data.frame(unique(complete_df$Address))
df3_new <- data.frame(unique(df_3$Address))

# converting from factor to character
cmp_df$unique.complete_df.Address. <- as.character(cmp_df$unique.complete_df.Address.)

df3_new$unique.df_3.Address. <- as.character(df3_new$unique.df_3.Address.)

#rename
colnames(cmp_df) <- c("place")
colnames(df3_new) <- c("place")

# verifying structure is correct (character)
str(cmp_df)
str(df3_new)

# 7 rows of missing data
## This is because these restaurants did not have menu data available to pull
## Need to remove from data; will use complete_df (111 restaurants) going forward
missing_data <- anti_join(df3_new, cmp_df, by = "place")
missing_data
```


# Fixing an Address String and Saving the Complete Data Frame
```{r}
# Checking for a particular address string
complete_df[complete_df$Address %like% "Location",]

# Fixing the address (says "Location Varies", but still pulls correct address info. Updating address.)
complete_df <- complete_df %>% 
  mutate(., Address = recode(Address, "'Location Varies Boston, MA, 02201' = '15 Court Square, Boston, MA 02108'"))

#write.csv(complete_df, "~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/complete_df.csv")

# this will preserve the proper format for the variables
#saveRDS(complete_df, "~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/complete_df")

# This data frame has each unique restaurant address to use for mapping in the app.
complete_df_app <- data.frame(unique(complete_df[,c(2,3,6:9)]))

#write.csv(complete_df_app, "~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/complete_df_app.csv")

# this will preserve the proper format for the variables
#saveRDS(complete_df_app, "~/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/complete_df_app")
```

The address pulled is labeled as "Location Varies Boston, MA, 02201"; however, the actual address being pulled is "15 Court Square, Boston, MA 02108". I updated the address in the data frame so the map in the app will display this address instead.
