---
title: "Map"
author: "John Viviani"
date: "4/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(leaflet)
library(dplyr)
library(stringr)
```

I'll use boston_add since it has the latitude and longitude for each restaurant, and then use df_boston to add information regarding the restaurant on each marker (e.g. name, address, cuisine, etc.). Likewise for Portland.

# Reading in the data
```{r}
# boston_add contains the coordinates
boston_add <- read.csv("C:/Users/JVivs/Documents/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/raw/boston_addresses.csv")
# df_boston has the restaurant names and cuisine
df_boston <- read.csv("C:/Users/JVivs/Documents/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/raw/df_boston.csv")
# menu data
boston_final <- read.csv("C:/Users/JVivs/Documents/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/boston_final.csv")

# portland_add contains the coordinates
portland_add <- read.csv("C:/Users/JVivs/Documents/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/raw/portland_addresses.csv")
# df_portland has the restaurant names and cuisine
df_portland <- read.csv("C:/Users/JVivs/Documents/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/raw/df_portland.csv")
# menu data
portland_final <- read.csv("C:/Users/JVivs/Documents/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/portland_final.csv")

# charleston_add contains the coordinates
charleston_add <- read.csv("C:/Users/JVivs/Documents/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/raw/charleston_addresses.csv")
# df_charleston has the restaurant names and cuisine
df_charleston <- read.csv("C:/Users/JVivs/Documents/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/raw/df_charleston.csv")
# menu data
charleston_final <- read.csv("C:/Users/JVivs/Documents/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/charleston_final.csv")

```


# Making a map of Boston
```{r}
boston_add %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions(), 
             popup = paste(df_boston$Restaurant, "<br>",
                           df_boston$Cuisine, "<br>",
                           df_boston$Address)) -> boston_map

boston_map
```

Let's merge the Boston and Portland dfs together to make a collective map.

# Making a map of Boston and Portland
```{r}
# binding df_boston and df_portland (contains restaurant info)
df_combined <- rbind(df_boston, df_portland)

# binding boston_add and portland_add (contains coordinates)
test <- rbind(boston_add, portland_add)

test %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions(), 
             popup = paste(df_combined$Restaurant, "<br>",
                           df_combined$Cuisine, "<br>",
                           df_combined$Address)) -> combined_map

combined_map
```

# Making a map of Boston, Portland, and Charleston
```{r}
# binding each city's restaurant info
df_3 <- rbind(df_boston, df_portland, df_charleston)

# check for these strings, and attach the corresponding city name
df_3 %>%
  mutate(City = case_when(grepl(', MA', df_3$Address) ~ 'Boston', 
                          grepl(', ME', df_3$Address) ~ 'Portland', 
                          grepl(', SC', df_3$Address) ~ 'Charleston')) -> df_3

# saving for use in app
#write.csv(df_3, "C:/Users/JVivs/Documents/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/df_3.csv")

# binding each city's coordinate info
df_3_coord <- rbind(boston_add, portland_add, charleston_add)

# attaching city column to df_3_coord as well
df_3_coord %>%
  mutate(City = case_when(grepl(', MA', df_3_coord$Address) ~ 'Boston', 
                          grepl(', ME', df_3_coord$Address) ~ 'Portland', 
                          grepl(', SC', df_3_coord$Address) ~ 'Charleston')) -> df_3_coord

# saving for use in app
#write.csv(df_3_coord, "C:/Users/JVivs/Documents/COLLEGE/GRAD SCHOOL/Capstone/Restaurant_App/data/processed/df_3_coord.csv")

df_3_coord %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions(), 
             popup = paste(df_3$Restaurant, "<br>",
                           df_3$Cuisine, "<br>",
                           df_3$Address)) -> map_3_cities

map_3_cities
```
